\chapter{Concept/Storyline}

\begin{center}
\emph{
They seek him here, they seek him there, \\
Those Frenchies seek him everywhere. \\
Is he in heaven or is he in hell? \\
That damned elusive Pimpernel.
}
\end{center}

%---
\section{Introduction}

The year is 1793. In France, the revolution has reached its zenith. The jails are full, as thousands of ``enemies of the revolution'' suffer Robespierre's Grande Terreur and the dreaded guillotine. Citizen denounces citizen, and everywhere cries of horror fill the air as more heads roll.

In this time of darkness, one man stands tall against the forces of evil - but no-one knows his name. As mysterious as he is legendary, the Scarlet Pimpernel will risk life and limb time and again to rescue the innocent from the brink of death - unless they catch him...

%---
\section{Description}

\emph{The Scarlet Pimpernel} is a first-person sneaker for PC. In it, you play Baroness Orczy's character Sir Percy Blakeney -- better known as the Scarlet Pimpernel -- as he rescues French aristocrats from the guillotine during the French revolution. (Note in passing that the original story has to the best of my knowledge now passed into the public domain, so there are no copyright issues involved.) You will break into French jails, perform daring rescues in the town squares of Paris, make crazy getaways from pursuing French soldiers, and generally cause as much irritation and discomfort as possible to Maximilien Robespierre and Citizen Chauvelin, all the while keeping your identity a closely-guarded secret. In between rescues, you will attend an English royal ball and sneak around in search of information, taking care to throw Chauvelin and his lackeys off your scent, not to mention your wife Marguerite and the royal guards. As the game progresses, it will become harder and harder to keep your identity a secret, until you are eventually discovered and thrown into the Bastille. For the finale of the game, you will make a daring escape with Marguerite across the rooftops of Paris to escape a horde of angry French peasants.

%---
\section{Key Features}

\begin{itemize}
\item Play as the legendary Scarlet Pimpernel and rescue aristos from the chop!
\item Use the shadows to your advantage as you work your nefarious business
\item Avoid the suspicions of the ever-watchful Chauvelin
\item Flee the vengeful Paris mobs as you make your escape!
\end{itemize}

%---
\section{Genre}

First-Person Sneaker (along the lines of the \emph{Thief} series)

%---
\section{Platform}

The engine itself is initially Windows-only (but the code is relatively portable as it uses only standard C++ and portable libraries). The map editor was written in Java and is thus multi-platform.

%---
\section{Characters}

\subsection*{Percy Blakeney}

Sir Percy Blakeney is an English nobleman with a secret. In public, he is a fop: a dandy who entertains the royal court with his own particular brand of risqu\'e humour. In private, he is the Scarlet Pimpernel: a daredevil rescuer of French aristos scheduled for the chop. As at ease fighting off hordes of crazed French guards as he is twirling around the dance floor, Percy's only fear is that he may be unmasked before his task is complete. To that end, he has kept his identity as the Pimpernel secret even from his wife Marguerite -- a former French republican actress whom he has yet to entirely trust after learning that her denunciation sent his friend the Marquis de St. Cyr and his family to the guillotine.

\subsection*{Chauvelin}

Citizen Chauvelin is Percy's great nemesis. A mid-ranking Republican with great ambition, he will stop at nothing to capture the Pimpernel -- but his first loyalty is always to himself and his own interests, not to the revolution.

\subsection*{Marguerite Blakeney}

Marguerite Blakeney was formerly Marguerite St. Just, an actress entertaining the masses in the new French republic. Now disillusioned with the revolution and married to Percy, she is yet to learn of his true identity. Instead, she merely sees him as an arrogant bore.

\subsection*{Maximilien Robespierre}

Maximilien Robespierre is the \emph{de facto} leader of the French revolution at this point in time. Formerly a lawyer in Arras, his supporters called him the `Incorruptible'. Now, as head of the Committee of Public Safety -- effectively the governing body of France at the time -- Robespierre has instituted \emph{la Terreur}, with thousands of `enemies of the revolution' sent to the guillotine.

\subsection*{The Prince Regent}

TODO

\subsection*{Armand St. Just}

TODO
